---
title: "Problem Statement 3"
author: "Apoorva Sood - 212410016"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

**Clearing the environment**

```{r}
rm(list=ls())
```

**Libraries Used**

```{r, warning=FALSE}
library(readxl)
library(outliers)
library(Rcmdr)
library(Metrics)
library(car)

```

**Importing the file and removing S.No column**

```{r}
data = read.csv("E:\\MY WORK\\Internship\\STEP i- Data Analytics and Machine Learning\\TASK - II\\Problem Statement 3 (ML)\\Data_file.csv")
View(data)
data= data[2:9]
```

**Getting the summary and structure of the data**

```{r}
summary(data)

```

*Converting characters in factors*

```{r}
str(data) #Has 3 variables with character datatype. We need to change them into factor for the analysis
data$College = as.factor(data$College)
data$Role = as.factor(data$Role)
data$City.type = as.factor(data$City.type)
```

```{r}
str(data)
```

**Checking for outlier in the data**

```{r}

hist(data$Previous.CTC)

```

**Model Building (Eliminating insignificant varaibles with BIC method)**

```{r}
attach(data)
data1 = lm(CTC~., data =data)

check = stepwise(data1, direction= "backward/forward",criterion = "BIC")

#We got 5 significant variables after Backward Elimination Method
model = lm(CTC~College + Role + City.type+ Previous.CTC +Exp..Months., data= data)

summary(model)

```

**We got residuals for our model and now we need to check their normality.**

```{r}
pred = predict(model)
res = residuals(model)
hist(res)
```

```{r}
#which =2 means qq plot #which =1 is the residual plot
plot(model, which=2, col=c("red")) 
```

**Checking normality and autocorrelation between the residuals**

**Normality test for variables**

-   NULL = The variable is normally distributed

-   ALTERNATIVE = The variable is not normally distributed

-   If p value is less than 0.05 (level of significance) then we reject the null hypothesis.

```{r}
shapiro.test(residuals(model)) #The residuals are not normally distributed.

durbinWatsonTest(model)#There is no autocorrelation amongst the residuals
```


**Predicting the CTC with model build using the train data**
```{r}
newdata = read.csv("C:\\No Dropbox\\Internship\\STEP i- Data Analytics and Machine Learning\\TASK - II\\Problem Statement 3 (ML)\\Test_data_file.xlsx - Prediction.csv")
View(newdata)
```

**Converting the character variables into factor**
```{r}
newdata$College = as.factor(newdata$College)
newdata$Role = as.factor(newdata$Role)
newdata$City.type = as.factor(newdata$City.type)


```


```{r}
str(newdata)
newdata$Predicted.CTC = predict(model, newdata)
View(newdata)


```

**Calculating the root mean squared error**
```{r}
attach(newdata)
model2 = lm(Actual.CTC~., data=newdata)
durbinWatsonTest(model2) #residuals are not auto-correlated



sqrt(mean(model2$residuals^2))
  
```


